Learning Discrete Bayesian Networks from Continuous Data

### 2015-12-01 BN_discretizer_paper.tex
updated bib
Change plot name
minor

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%\begin{filecontents*}{example.eps}
  %!PS-Adobe-3.0 EPSF-3.0
  %%BoundingBox: 19 19 221 221
  %%CreationDate: Mon Sep 29 1997
  %%Creator: programmed by hand (JK)
  %%EndComments
%  gsave
%  newpath
%    20 20 moveto
%    20 220 lineto
%    220 220 lineto
%    220 20 lineto
%  closepath
%  2 setlinewidth
%  gsave
%    .4 setgray fill
%  grestore
%  stroke
%  grestore
%\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{tikz}
\usepgfplotslibrary{groupplots}
\usepackage{lscape}
\usepackage{caption}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{boondox-cal} % for lowercase caligraphic
\usepackage[font=small,skip=5pt]{caption}
\usepackage[hyphens]{url}

\usetikzlibrary{bayesnet}
\setcitestyle{aysep={ }} %Author-Year Separator
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\pgfplotsset{
    jitter/.style={
        x filter/.code={\pgfmathparse{\pgfmathresult+rnd*#1}}
    },
    jitter/.default=0.1
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CUSTOM COMMANDS

@@

Equation~\ref{eqn:MDL} can be minimized exactly using dynamic programming.
For a given Bayesian network, the first three terms only depend on the number of discretization intervals $|X|$ and the fourth term is cumulative over the intervals.
Hence, if $\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}$ is a MDL optimal discretization policy with $k$ intervals, then $\Lambda' = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_{k-1}}$ is a MDL optimal discretization policy for the corresponding subproblem with $k-1$ intervals.
This procedure takes runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$.
All variables are defined in Section \ref{subsec:algo}.
Therefore, the runtime of the proposed method in this paper is shorter than the MDL discretization method by $\bigo \paren{n^3}$, since the former has a more efficient form of dynamical programming.

@@

\begin{table}[ht]
  \centering
  \caption{
    The discretization policies for the Auto MPG dataset with the fixed structure shown in Figure~\ref{fig:auto_graph_3}.
    The first five rows list the discretization edges for each continuous variable.
    The last row shows the mean cross-validated log-likelihood under each policy.
    The methods have the same discretization for variable $A$, and the log-likelihood for the Bayesian method is only slightly better than that for the MDL method.
  }
\input{table_autoMPG_3.tex}
  \label{table:auto_disc_table_3}
\end{table}
\end{document}
% end of file template.tex

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
%\begin{filecontents*}{example.eps}
  %!PS-Adobe-3.0 EPSF-3.0
  %%BoundingBox: 19 19 221 221
  %%CreationDate: Mon Sep 29 1997
  %%Creator: programmed by hand (JK)
  %%EndComments
%  gsave
%  newpath
%    20 20 moveto
%    20 220 lineto
%    220 220 lineto
%    220 20 lineto
%  closepath
%  2 setlinewidth
%  gsave
%    .4 setgray fill
%  grestore
%  stroke
%  grestore
%\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[round]{natbib}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{tikz}
\usepgfplotslibrary{groupplots}
\usepackage{lscape}
% \usepackage{caption}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{BOONDOX-cal} % for lowercase caligraphic
\usepackage[font=small,skip=5pt]{caption}
\usepackage[hyphens]{url}

\usetikzlibrary{bayesnet}
\setcitestyle{aysep={ }} %Author-Year Separator
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

\pgfplotsset{compat=1.11}
\pgfplotsset{
    jitter/.style={
        x filter/.code={\pgfmathparse{\pgfmathresult+rnd*#1}}
    },
    jitter/.default=0.1
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CUSTOM COMMANDS

@@

The global minimum of Equation~\ref{eqn:MDL} can be found using using dynamic programming.
For a given Bayesian network, the first three terms only depend on the number of discretization intervals $|X|$ and the fourth term is cumulative over the intervals.
Hence, if $\Lambda = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_k}$ is a MDL optimal discretization policy with $k$ intervals, then $\Lambda' = \anglebrackets{\gamma_1, \gamma_2, \ldots, \gamma_{k-1}}$ is a MDL optimal discretization policy for the corresponding subproblem with $k-1$ intervals.
This procedure takes runtime $\bigo \paren{ n^3 + \paren{ n_c \cdot {L}^{n_s}  + {L}^{n_p}} \cdot n^2 }$.
All variables are defined in Section \ref{subsec:algo}.
Therefore, the runtime of the proposed method in this paper is shorter than the MDL discretization method by $\bigo \paren{n^3}$, since the former has a more efficient form of dynamical programming.

@@

\begin{table}[ht]
  \centering
  \caption{
    The discretization policies for the Auto MPG dataset with the fixed structure shown in Figure~\ref{fig:auto_graph_3}.
    % The first five rows list the discretization edges for each continuous variable.
    % The last row shows the mean cross-validated log-likelihood under each policy.
    The methods have the same discretization for variable $A$, and the log-likelihood for the Bayesian method is only slightly better than that for the MDL method.
  }
\input{table_autoMPG_3.tex}
  \label{table:auto_disc_table_3}
\end{table}
\end{document}
% end of file template.tex
